---
title: "scrapingChessCom"
author: "Baptiste Toussaint"
date: "2024-03-06"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Scraping Data from Chess.com API

API's documentation :
https://www.chess.com/news/view/published-data-api#pubapi-general

This notebook scrap informations about titled players from *Chess.com*.
Existing title are (see [article](https://www.chess.com/terms/chess-titles)
about title):

- Grandmaster (GM)
- International Master (IM)
- FIDE Master (FM)
- Cadidate MAster (CM)
- Woman Grandmaster (WGM)
- Woman International Master (WIM)
- Woman FIDE Master (WFM)
- Woman Candidate Master (WCM)
- National Master (NM)
- Woman National Master (WNM)

## Scraping

```{r}
# Library for web scraping
library(httr)
library(jsonlite)
library(readr)
library(tibble)
```

```{r}
# valid title used by API
titles <- c("GM", "WGM", "IM", "WIM", "FM", "WFM", "NM", "WNM", "CM", "WCM")
chess_url_get_player_list <- "https://api.chess.com/pub/titled/"
chess_url_get_player_info <- "https://api.chess.com/pub/player/"
```

```{r}

scrap_url <- function(url) {

  # Get 'content' of the GET method.

  url_content <- toJSON(
    fromJSON(content(GET(url), as = "text", encoding = "UTF-8")),
    pretty = TRUE
  )
  
  return(url_content)
}

retrieve_info_from_player_username <- function(username) {
  
  # Get all the information from one user
  
  return(
    c(
      fromJSON(scrap_url(paste(chess_url_get_player_info,username,sep=""))),
      fromJSON(scrap_url(paste(chess_url_get_player_info,username,"/stats/",sep="")))
    )
  )
}
```

```{r}
# Get list of titled player from Chess.com
players_list <- c()
for (title in titles) {
  players_list <- c(
    players_list,
    # fromJSON(scrap_url_to_json(paste(chess_url_get_player_list,title,sep="")))$player
    fromJSON(scrap_url(paste(chess_url_get_player_list,title,sep="")))$player
  )
}
```

```{r}
# Test JSON
file_name <- "test.json"
for (name in players_list) {
  write(
    toJSON(retrieve_info_from_player_username("hikaru"),pretty = TRUE),
    file = file_name,
    append = TRUE
  )
}
```


